PCA

### 2019-10-18 analysis/04_DESeq2_sexes.Rmd
new pca new ms

```{r setup, include = FALSE}

library(tidyverse)
library(DESeq2)
library(cowplot)
library(pheatmap)
library(viridis)
library(forcats)
library(caret) # LDA analysis
library(MASS) # LDA analysis
library(ggtext) # for pretty plots
library(ctsGE)

@@

@@

# gonad
plotWGCNAcandidates(vsd.gon, c("NP_989957.1", "NP_001120784.1", "NP_001120786.1",
                               "NP_001131120.1", "NP_001186037.1", "NP_989871.1",
                               "NP_990797.2", "XP_015132722.1"), colDataGon, "Gonad: CISH, SOCS, PRL, PRLR")
```

>>>>

```{r setup, include = FALSE}
library(tidyverse)
library(DESeq2)
library(cowplot)
library(pheatmap)
library(viridis)
library(forcats)
library(caret) # LDA analysis
library(MASS) # LDA analysis
library(ggtext) # for pretty plots
library(ctsGE)

@@

# genes from https://link.springer.com/article/10.1007%2Fs12079-012-0168-0
# A pathway map of prolactin signaling
# PL, RAC1, IRS2 not found
plotWGCNAcandidates(vsd.pit, c("NP_990797.2", "XP_015132722.1", "NP_989690.1",
                               "NP_001025709.2", "XP_015144878.1", "NP_989481.1",
                               "NP_001186467.1", "NP_990386.1", "XP_015132490.1",
                               "XP_417614.3", "XP_015150421.1", "NP_001155844.1"), 
                    colDataPit, "Pit: Genes involved in prolactin signaling")

@@

plotWGCNAcandidates(vsd.hyp, c("NP_990797.2", "XP_015132722.1", "NP_989690.1",
                               "NP_001025709.2", "XP_015144878.1", "NP_989481.1",
                               "NP_001186467.1", "NP_990386.1", "XP_015132490.1",
                               "XP_417614.3", "XP_015150421.1", "NP_001155844.1"), 
                    colDataHyp, "Hyp: Genes involved in prolactin signaling")

# gonad
plotWGCNAcandidates(vsd.gon, c("NP_989957.1", "NP_001120784.1", "NP_001120786.1",
                               "NP_001131120.1", "NP_001186037.1", "NP_989871.1",
                               "NP_990797.2", "XP_015132722.1"), colDataGon, "Gonad: CISH, SOCS, PRL, PRLR")

plotWGCNAcandidates(vsd.gon, c("NP_990797.2", "XP_015132722.1", "NP_989690.1",
                               "NP_001025709.2", "XP_015144878.1", "NP_989481.1",
                               "NP_001186467.1", "NP_990386.1", "XP_015132490.1",
                               "XP_417614.3", "XP_015150421.1", "NP_001155844.1"), 
                    colDataGon, "Gonad: Genes involved in prolactin signaling")

### 2019-10-18 analysis/11_pcalda.Rmd
new pca new ms

```{r pca}
pseudocounts <- read_csv("../results/01_pseudo.counts.csv")

colData <- read.csv("../metadata/00_colData_characterization.csv", header = T, row.names = 1)
colData$treatment <- factor(colData$treatment, levels = 
                              c("control",  "bldg", "lay", "inc.d3", "inc.d9", "inc.d17", 
                                "hatch", "n5", "n9"))

geneinfo <- read.csv("../metadata/00_geneinfo.csv", row.names = 1)

@@

countData <- subsetcounts(colData, pseudocounts)

@@

mypcadf <- data.frame(PC1 = mypca$x[, 1], PC2 = mypca$x[, 2], PC3 = mypca$x[, 3], 
                  PC4 = mypca$x[, 4],PC5 = mypca$x[, 5],PC6 = mypca$x[, 6],
                  ID = row.names(countData))

mypcadf$V1 <- row.names(mypcadf)
mypcadf <- left_join(colData, mypcadf)

a <- ggplot(mypcadf, aes(x = PC1, y = PC2, color = colData$treatment)) +
  geom_point() + labs(x = "PC1: 35.9%", y = "PC2: 32.5%") + theme_minimal(base_size = 8)  +
  theme(legend.title = element_blank(), legend.position = "left")

b <-  fviz_pca_var(mypca,  labelsize = 3 , axes.linetype = "blank")

ab <- plot_grid(a,b + theme(axis.text = element_blank()) + ggtitle(NULL), rel_widths = c(0.6,0.4))
ab

>>>>

```{r pca}
pseudocounts <- read_csv("../results/01_pseudo.counts.csv")
head(pseudocounts[1:3])

colData <- read.csv("../metadata/00_colData_characterization.csv", header = T, row.names = 1)
colData$treatment <- factor(colData$treatment, levels = 
                              c("control",  "bldg", "lay", "inc.d3", "inc.d9", "inc.d17", 
                                "hatch", "n5", "n9"))
head(colData[1:3])

geneinfo <- read.csv("../metadata/00_geneinfo.csv", row.names = 1)
head(geneinfo)

@@

countData <- subsetcounts(colData, pseudocounts)
head(countData[1:3])

@@

mypcadf <- data.frame(PC1 = mypca$x[, 1], PC2 = mypca$x[, 2], PC3 = mypca$x[, 3], 
                  PC4 = mypca$x[, 4],PC5 = mypca$x[, 5],PC6 = mypca$x[, 6],
                  ID = row.names(countData))
mypcadf$V1 <- row.names(mypcadf)
mypcadf <- left_join(colData, mypcadf)
mypcadf <- mypcadf %>% select(bird,sex,tissue,treatment,PC1:PC6)
head(mypcadf)

a <- ggplot(mypcadf, aes(x = PC1, y = PC2, color = colData$treatment)) +
  geom_point() + labs(x = "PC1: 35.9%", y = "PC2: 32.5%") + theme_minimal(base_size = 8)  +
  theme(legend.title = element_blank(), legend.position = "left")
a

b <-  fviz_pca_var(mypca,  labelsize = 3 , axes.linetype = "blank", 
                   repel = TRUE ,
                  select.var= list(contrib = 10))
b

ab <- plot_grid(a,b + theme(axis.text = element_blank()) + ggtitle(NULL), rel_widths = c(0.6,0.4))
ab
```
